Correlation Clustering with Dynamic Super-Nodes (DySNCC)

### 2014-10-13 paper/egpaper_for_review.tex
add tables
paper mine

The edge weighted watershed algorithm
with random seeds can be used to get 
cheap proposals.

>>>>

The edge weighted watershed algorithm \cite{meyer_2013}
with random seeds can be used to get 
cheap proposals. Instead of $n$ seeds distributed uniformly
over all nodes we use the following.
Draw $n/k$ random edges only the negative edges, 
and give the two nodes of each random edge different seeds.
Doing so, a random subset of negative edges is forced
to be cut within each proposal.
For additional randomness, noise can be added to
the edge weighs.
